Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks

### 2023-07-07 methods/subsections/implementation.tex
Updates from Overleaf

Introduced by Bromley and LeCun \cite{Bromley1993SignatureNetwork}, Siamese Networks are deep learning architectures designed for tasks requiring comparison or similarity assessment between instances. The architecture comprises identical subnetworks that share the same parameters, improving memory usage and computational efficiency. Rather than learning specific features of individual classes, they focus on a similarity metric, making them ideal for imbalanced datasets. Each subnetwork processes an input independently, combining the outputs to yield a similarity score. Training with shared weights enables the model to learn invariant input representation, improving comparison efficiency. This is accomplished through a specialized loss function called triplet loss, which aims to minimize the distance between similar inputs and maximize it for dissimilar ones.

@@

\begin{table}[ht]
\centering
\small
\begin{tabularx}{\textwidth}{
  >{\centering\arraybackslash\hsize=1.6\hsize}X
  >{\centering\arraybackslash\hsize=0.6\hsize}X
  >{\centering\arraybackslash\hsize=0.6\hsize}X}
\toprule
\thead{\textbf{Layer Type}} & \thead{\textbf{In Channels}} & \thead{\textbf{Out Channels}} \\
\midrule
Conv + ReLU & 1 & 128 \\
\addlinespace
\multirow{9}{*}{Conv + BatchNorm + ReLU + MaxPool} & 128 & 128 \\
\addlinespace
 & 128 & 128 \\
\addlinespace
 & 128 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 512 \\
\addlinespace
Conv + BatchNorm + ReLU + AvgPool & 512 & 512 \\
\addlinespace
Fully connected layer & 512 & 128 \\
\bottomrule
\end{tabularx}
\caption{Layer specifications for the SampleCNN model}
\label{tab:samplecnntable}
\end{table}

@@

@@

\subsection{Loss function}

>>>>

Introduced by Bromley and LeCun \cite{Bromley1993SignatureNetwork}, Siamese Networks are deep learning architectures designed for tasks requiring comparison or similarity assessment between instances. The architecture comprises identical subnetworks that share the same parameters, improving memory usage and computational efficiency. Rather than learning specific features of individual classes, they focus on a similarity metric, making them ideal for imbalanced datasets. Each subnetwork processes an input independently, combining the outputs to yield a similarity score. Training with shared weights enables the model to learn invariant input representation, improving comparison efficiency. This is accomplished through a specialized loss function called triplet loss, which aims to minimize the distance between similar inputs and maximize it for dissimilar ones. The loss function will be explained later in Subsection~\ref{subsec:loss-function}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}
    \centering
    \includegraphics{figures/images/applsci-08-00150-g001.png}
    \caption[]{Caption}
    \label{fig:enter-label}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[ht]
\centering
\small
\begin{tabularx}{\textwidth}{
  >{\centering\arraybackslash\hsize=0.5\hsize}X
  >{\centering\arraybackslash\hsize=0.25\hsize}X
  >{\centering\arraybackslash\hsize=0.25\hsize}X}
\toprule
\thead{\textbf{Layer Type}} & \thead{\textbf{In Channels}} & \thead{\textbf{Out Channels}} \\
\midrule
Conv + ReLU & 1 & 128 \\
\addlinespace
\multirow{9}{*}{Conv + BatchNorm + ReLU + MaxPool} & 128 & 128 \\
\addlinespace
 & 128 & 128 \\
\addlinespace
 & 128 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 256 \\
\addlinespace
 & 256 & 512 \\
\addlinespace
Conv + BatchNorm + ReLU + AvgPool & 512 & 512 \\
\addlinespace
Fully connected layer & 512 & 128 \\
\bottomrule
\end{tabularx}
\caption{Layer specifications for the SampleCNN model}
\label{tab:samplecnntable}
\end{table}

@@

In conclusion, raw audio waveforms were our final choice for input for the anchor. Each input sequence was 15 seconds long, roughly equivalent to 8 bars of 4/4 music at 120 beats per minute. The audio was sampled at a frequency of 16 kHz, a decision influenced by the requirements of SampleCNN, computational resources, and our belief in the value of high-resolution data for revealing a comprehensive picture of the audio content. We are confident that this choice of input contains a significant amount of meaningful musical information. Although it may not encompass the complexity of a symphony, it is sufficient for the scope of our experiments.

@@

\subsection{Loss function}
\label{subsec:loss-function}
